A quantitative framework for investigating the reliability of empirical network construction

### 2018-11-27 manuscript/reply_to_reviewers.tex

\begin{document}

\newpage

\setcounter{page}{1}

Changes: reducing discussion of different sources of uncertainty, increasing description of priors, added a bunch of refs, trying to frame our study more clearly.

Still to do: framing, expand discussion of network metrics from sampled vs. predicted vs. expert knowledge networks... (ours reflect about 50\% of links observed, doesn't seem super out of line). Make clearer that we are modelling L but could also model X|L with independent $n$ and $k$ data within a single site. Maybe in the section introducing the model or introducing the case study?

Ask for help: how would we expand this to interaction frequencies? Still with the Bernoulli?
% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Associate Editor}
% ---------------------------------------

@@

\newpage

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Reviewer \#1}
% ---------------------------------------

	1. Suggestion to refocus on prior selection [[not done]]

		\begin{refquote}
			Below I offer my thoughts on this well-written manuscript. Normally I condense my review into a few key points, but I found myself uncharacteristically divided with the paper as presented. At first, the introduction covers ground very well-trod by prior works and doesn’t really address its contribution. I was mostly frustrated by the rehashing of topics made by many previous papers, include many by the authors themselves. But then the paper seems to morph and pick up steam on L248. Rather than reaching towards an amorphous and grandiose “quantitative framework”, the authors briefly zoom into a very concise, and hugely important, question of choosing prior distributions for harnessing information among networks. This has been completely unexplored and merits attention. In ecology more broadly, priors are treated with timidity, as if we couldn’t dare to leverage past work on our current understanding. Personally, I have always felt limited by this standard. I applaud the authors for taking on this challenge, and I would like to see an introduction that merits and debates this question in much more detail. When should we use prior information? How do we go about constructing informed priors for networks? When can we use priors from the data in question? This is sometimes called approximate bayes (http://andrewgelman.com/2016/03/25/28321/), or empirical bayes, perhaps alluded to in the title, but not fully explained in the introduction. Should empirical priors be drawn from hyperpriors or fixed for each interaction? Can we combine qualitative information and quantitative information? This is all exciting ground that will open up new avenues for networks. Walking the reader through flat priors, informed priors and empirical priors is crucial for the importance of analysis to be understood by the reader. The use of empirical priors can be quite controversial, and should be atleast touched on in the discussion. \\
			I’ve left my comments below on the introduction, but in my opinion, it should be almost wholly rewritten in favor of a more targeted question constructing networks using priors, which is the key novelty of the work and is mostly hidden by the current introduction. I’m not convinced any new analysis needs to be done, which speaks to the conflict between the current introduction and the actual data presented. I see the makings of a really nice paper here, and I’m confident the authors will be able to achieve this text revision.
			\medskip
			At the same time, the paper is clear and very readable. I wholly support the method and I think it is something critical that needs to be adopted by the community. \\
			Having read the paper several times, I think that the authors are trying to cast their net too widely, even starting from the title. From that perspective, they don’t meet the expectation of new insight. However!! I was extremely interested in the brief discussion on using prior knowledge, especially the delicacy of trying to transfer information among networks (L248). My recommendation is to drastically reduce the grandiose attempt at a “quantitative framework for networks” (L1 – L246) and really zoom in on the contribution of transferring information among networks through informed priors.	Again L278, this is very well covered in concept by recent papers in MEE that include the authors of this work, as well as several by Weinstein, Bartomeus and others.
			\end{refquote}

@@

		\textbf{R:} We thank the Reviewer for the suggestion to expand our discussion of prior selection, particularly with regard to approxmimate/empirical bayes. [[Expand refs to this]] We now walk through flat, informed, and empirical priors as suggested (lines XX-XX) and refer to the controversy surrounding empirical priors in our discussion (lines XX-XX).\\
			We also appreciate the Reviewer's comments on our introduction. We feel that understanding the problem of uncertain detection of interactions is important motivation for a reader not already familiar with Bayesian procedures to wade through a larger discussion on priors. Therefore we have revised and, hopefully, streamlined our discussion but do not jump straight in to priors. We have, however, taken care to introduce our analysis as a worked example (lines XX-XX) and hope that this helps to reduce the conflict between the introduction and our data. [[Add something else about different priors? Add different priors to our analyses?]]
			[[Definitely should expand this, but do we want to really focus on those?]][[not quite done]]

			We thank the Reviewer for their compliments and accept their suggestion that we are somewhat overexcited about our approach. We have refined the introduction to be more specific about the problem we are attempting to solve. We have also expanded our treatment of prior selection and hope that our paper now reads as achieving its goal.

	2. Suggestion to add more literature [[done]]

@@

		\textbf{R:} While we feel that a short introduction to the beta distribution is important to bring researchers new to Bayesian statistics up to speed (and give them some keywords to Google), we accept the Reviewer's suggestion to reduce the amount of space given to the beta. We have therefore moved the description of basic properties to Appendix S2. The remaining paragraph introducing the beta distribution now leads directly into the section describing prior selection.

	5. Novelty of the study not clear in current framing [[not done? Done? Clearer?]]

		\begin{refquote}
		I’m wrestling with the novelty of the work as presented and whether it reaches the standard for publication at MEE. Certainly, much of this logic is laid out in other works. The authors are well aware of this and have made significant contributions to this topic in the last few years. In particular, the authors should try to be much more explicit about the contribution they hope to offer that hasn’t been covered. ...
		While it is true that none of the [suggested] papers do the exact same thing as this manuscript, they all	orbit the same topic. 
		\end{refquote}

		\textbf{R:} We thank the Reviewer for the literature suggestions and now include them in our introduction and/or discussion. We emphasize the board applicability of our approach across network types and systems with varying degrees of prior knowledge. We also emphasize that our approach is not restricted to species observed X times (as many predictive models are) and can include species not yet observed at a site (e.g., potential invaders). We hope that the contribution our manuscript makes is now clearer.

@@

	Minor points:

	-l.62: define formally T
	-l.244: this is weird to mention that the analysis has been done on another dataset but that the results will not be discussed… What is the interest for the reader?
	-l.149: since the authors consider the interactions are independent, there is morally no network in the approach (except the result)
	-l.252: not clear. Why this choice?
	-l.259: not clear
	-l.278: the authors investigate the consequence of uncertainity on network metrics. This question is of peculiar interest, but here it is restricted to the connectance and nestedness. Why these two metrics? Why not others? What is the impact of integrating incertainity into the metrics computation? (we guess the answers but we could expect the authors develop these points).
	l.291: explain better the simulation procedure
	l.306: given the shape of the distribution (exponential), the mean is not an appropriate indicator.
	l.327: what does it mean? How is it possible?

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Referee \#3}
% ---------------------------------------

	\begin{refquote}
		Comments to the Corresponding Author
		Overall, I think this is a very good paper and makes an important contribution.  I think there are three main ways it can be improved: 1.      The simplest – do a better job of acknowledging what else has been done in the field – much of which has actually been done by the authors and their collaborators. ... 2.      Provide more clarity in descriptions making sure to consider how terms and ideas have been used previously. ... 3.      The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.
		I hope this review is helpful.

		More generally, the introduction does not really do justice to what has been done already – even the authors own work.  The problem in my view is that the community using better statistics – of which the authors are very important members – has not managed to communicate to most people studying networks and better methods are simply not being adopted.  The current paper is a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages.  I think this is a very important message and is what makes this paper an important contribution.  Further, the approach to parse out different types of uncertainty and suggestions for how to come-up with informative priors – is very useful.  The theory/method is well developed overall and provides an example – which is great.

@@

		\textbf{R:} We than the Reviewer for their literature suggestions and for demonstrating that our desire not to criticise hard-working empiricists could be misinterpreted as suggesting reduced sampling effort. We had not realised that anyone would consider such a possibility and have revised our manuscript to make it clearer that our approach is a complement to extensive sampling, not an excuse for poor sampling.

	1. Add more references to the literature [[done]]

		\begin{refquote}
		1.      The simplest – do a better job of acknowledging what else has been done in the field – much of which has actually been done by the authors and their collaborators.  Given that they know there work I won’t point that out (but they are under-siting this literature a bit) but they could consider Graham and Weinstein on-line early 2018 (I realize that this was just out when the author’s submitted but it has some very similar messages) and the empirical example of Weinstein and Graham in Ecology letters 2017.  I don’t think this would in any way diminish the importance of the current paper because I think the challenge in network ecology is to get people to use better quantitative methods.
		\end{refquote}

		\textbf{R:} We had not intended to write a review paper and did not wish to over-cite ourselves, but we take the Reviewer's point and have expanded our references to the literature. We have taken particular care to add references to Graham/Weinsten papers as two of the reviewers suggested work by these authors. We hope that the introduction now presents a more thorough sample of previous work.

@@

		\begin{refquote}
		Line 7.  It is certainly true that most networks are snapshots in time but there is a growing realization – including some nice examples (including those by the authors) that address this issue.  Maybe what you want to say is that we know that networks should not be considered static but we lack the tools – or ability to collect data – or whatever you think is the cause – to correct this situation. 
		\end{refquote}

		\textbf{R:} We have softened this statement to say that empirical networks are "often limited" and hope that this rephrasing will not offend those who are working to include variation in their descriptions.

			\begin{quotation}
				Despite this additional information, empirical descriptions of ecological networks are still often limited by a lack of data or tools to adequately incorporate variation in interactions into networks.
			\end{quotation}

		\begin{refquote}
		Line 30.  There are several conceptual and empirical attempts to consider detection probability – why aren’t these cited (work by Bartomeus comes to mind).\\
		\end{refquote}

			\textbf{R:} We have added a citation to Bartomeus as requested.

		\begin{refquote}
			Line 36.  I certainly see value in the approach and the general ideas of these authors in particular but they should acknowledge the work that has been done by themselves and others!\\
		\end{refquote}

		\textbf{R:} We have rephrased the end of this paragraph to mention previous predictive models dealing with uncertainty in interaction matrices.

		\begin{refquote}
		Line 89.  In Weinstein and Graham (Ecology Letters) the processes modeled were trait matching (which you place in interaction uncertainty) and abundance (which is perhaps your process uncertainty??).  I find myself quite confused based on how you describe things in this MS (See text above) and how you cite the literature.
		\end{refquote}

		\textbf{R:} We have revised this section and now no longer refer to the specifics of Weinstein and Graham at all. Instead, we discuss repeated sampling in a box dedicated to the question of whether sampling is useful (of course it is) and whether it can completely solve problems of uncertainty in ecological networks (almost certinaly not). We hope that this is less confusing.

		\begin{refquote}
		Line 148.  Please note that a paper with a very similar aim was recently published (Graham and Weinstein).  This does not to diminish the value of this study in any way, as multiple perspectives on quantitative solutions in network ecology are urgently needed….. but the other work should be considered. 
		\end{refquote}

		\textbf{R:} We had not seen the Graham and Weinstein paper when we first submitted our manuscript, but now cite it in the introduction. We have also revised this section in hopes of making the uniqueness of our framework (its simplicity and adaptability) clear.

		\begin{refquote}
		Line 288.  I am pretty sure this idea is in the literature several times and should be cited.  Isn’t this the same as drawing a probability of interaction from a distribution where the distribution of each interaction is an output of the Bayesian method?\\
		\end{refquote}

		\textbf{R:} Yes, that is exactly the idea. We are also sure that this is a common approach and therefore hadn't cited it (in the same way one would not be likely to cite the prior users of common statistical tests). We have added a citation to~\citet{Vazquez2005,Guimera2009} as two examples and hope that this is sufficient.

		\begin{refquote}
		Line 352 – 358.  Citations are needed in this section as this has been suggested before.
		\end{refquote}

		\textbf{R:} Most of these lines refer specifically to our results, making it somewhat difficult to add citations. We have added citations where possible and rephrased this section to make it clearer when we are referring to work done in the present manuscript.

	2. Confusing terminology [[done]]

@@

		\begin{refquote}
		2.      Provide more clarity in descriptions making sure to consider how terms and ideas have been used previously.  Two things come to mind – the use of terms and distinction between interaction and process uncertainty; and the somewhat contradictory sounding statements about if sampling more is actually good.
		\medskip
		Line 86.  So, similar factors (i.e., trait matching) can be used to detect different kinds of uncertainty.  Should this be stated?  You might also consider a different word that process as “observation models” and “process models” are commonly used terms in Bayesian stats and in this case “process” often considers what you call “interaction”.  There are some interesting to attempts to model co-evolution that consider similar ideas (i.e., a barrier to interaction and then trait-matching; but maybe outside of the scope of this MS). While I appreciate that your naming has merit, I think if your hope is that more ecologists use these methods then the terminology should be consistent across papers/approaches to the greatest extent possible.
		\end{refquote}

		\textbf{R:} We have revised this section of the introduction to both avoid introducing rigid terminology and make it clear that our model is not concerned with partitioning different sources of variation (indeed, we state that in many cases this is not possible using empirical data). Hopefully this will discourage readers from getting bogged down in trying to isolate which external factors cause which types of uncertainty (there is almost certainly overlap - e.g., bad weather could both reduce the probability that species will be active and interact and the probability that an interaction is observed if visibility is poor). We have also added a section (lines XX-XX) referring to "forbidden links" which address aspects of whether species can interact (which we had previously called interaction uncertainty) and whether they do interact at a particular site (previously process uncertainty). We hope that this addition clarifies the agreement of our manuscript with previous works listing sources of uncertainty.

        \textbf{Forbidden links}

            Both of the above sources of uncertainty (i.e., whether species would be able to interact given their traits and whether they are able to interact at a particular place and time) are addressed in the concept of "forbidden links"~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling~\citep{Jordano1987}, physiological constraints~\citep{Jordano1987,More2012}, etc. are considered "structural zeros" that cannot be observed~\citep{Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}. In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.

	3. Introduction of the case study seems off-topic and illogical. [[done]]

		\begin{refquote}
		3.      The set up (introduction) to the case study is quite odd and somehow seems off topic – or at least not logical based on what the reader has read up to that point.
		\medskip
		Line 240.  I found the justification for the system a bit odd.  Is the goal to show the gaps in sampling or to apply the model described thus far to consider the 3 different types of uncertainty outlined?  At this point the reader is confused about the goal…
		\medskip
		Line 249.  The statement about training data is redundant with what is stated above – adjust writing.
		\end{refquote}

		\textbf{R:} We have expanded our introduction of the case study (lines XX-XX) to make it clear that we are using the highest-quality empirical network we can find as even such networks have uncertainty about unobserved interactions. This relates back to our point that urging increased sampling effort is not likely to solve problems of uncertainty as long as sampling is limited in number of methodologies, biased towards abundant or easy-to-identify species, restricted to particular spatial sites and/or environmental conditions (if the network is intended to be more general), or all of the above. We repeat this point in the discussion to ensure that the case study is relevant. We have also clarified our statement that strict Bayes does not allow empirical priors, but that they are an option for researchers that are more concerned about matching their prior to their study system than with strict formalism (lines XX-XX). As Reviewer 1 points out, this is somewhat controversial and we feel it is important to note the potential objection.

 			To illustrate the process of constructing a Bayesian network to quantify uncertainty about interactions, we use the comprehensively-sampled system of willows (\emph{Salix}), herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S4} for details). 
      The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together. To show the gaps in sampling, we compared the frequencies of observed co-occurrences and interactions. We then calculated an empirical prior and computed the posterior distribution of the probability of observing each as-yet-unobserved interaction in the future.
      \medskip
			While a strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand, such data are not always available. In that case, researchers must choose between using a less-informative prior (e.g., one based on distributions of links across a large set of networks) or an empirical prior based on some "training data" from the study. 
		\end{quotation}

@@

		\begin{refquote}
		Line 107.  There is a lot of literature in wildlife ecology emphasizing the importance of repeat sampling for estimating detection probability.  Is this just wrong?  If so this does need more explanation in the context of this literature.
		\end{refquote}

		\textbf{R:} I do not know how the Reviewer assumes that we are against repeat sampling when this is, in fact, one of the core parts of our approach. Our point here is that some species (e.g., cryptic or difficult-to-identify species) and interactions (e.g., brief visits of pollinators to plants) are difficult to detect and may be missed even with multiple sampling. If a rare species is only detected in one sampling round, then the repeated sampling necessarily tells us little about its interactions. For species which are frequently detected, we absolutely learn about the detection probability of their interactions with repeated sampling.

		\begin{refquote}
		Line 130.  The ideas here are largely a repeat from those above.  Further, while it may be true that we can sample too much – I think it is dangerous to suggest we should sample less – do the authors think that sampling across most network studies is sufficient (the opposite is stated in the discussion)?  I wonder if the argument is a bit more statistical than biological.
		\end{refquote}

### 2018-11-27 manuscript/CI_interactions.tex
getting close to the end, except R2

    First and foremost, ecological communities are known to be stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence in interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}. Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012,Emer2018}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Fodrie2015,Novak2015}, throughout life cycles~\citep{Preston2014,Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}). An assessment of the accumulation of inter0actions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeeus2013,Poisot2016}. Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}. Such models provide an important ''reality check'' by allowing us to test hypotheses about the factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017.Weinstein2017a,Graham2018}. They can also allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.

    [[These two paragraphs try to frame our study more clearly. Any help to shorten them?]]
    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}). The general models may not include any system-specific information, while the system-specific models may not be applicable outside of their system of origin. Here we propose a simple Bayesian framework that can include broad general trends in network structure or highly specific expert knowledge, depending on the situation. This framework is designed to make the assumptions used when building networks more explicit and to quantify our uncertainty around each interaction in a network. Importantly, the simplicity of the framework means it should be easily applicable to any network type or study system.

    First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction. In the context of this uncertainty, which can be reduced but usually not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomes2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure. We conclude with a worked example applying this framework to an intensively-sampled willow-galler network. We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks. We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks.

@@

          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not~\citep{Poisot2015}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L|\mathbf{T}) = \lambda$~\citep{Gravel2013,others}. 
          In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda$.
          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}. Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{}. These examples show that we often cannot say that an interaction absolutely does not occur. Instead, an unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016}. As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. Until these gaps are filled, some uncertainty will remain about whether some species pairs could interact.

@@

          Assuming that an interaction is feasible (i.e., $L=1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}. This could be because the two species do not co-occur or, if they did occur, because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a more preferred interaction partner was available~\citep{Weinstein2017a}, or substantial individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Poisot2015}. For example, a rare galler may not parasitize a rare plant because they do not encounter each other. 
          We can define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. It is unlikely that $\chi=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur. When $\chi<1$ we cannot be sure whether an unobserved interaction did not occur and when it occurred but was not observed.

@@

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it~\citep{Jordano2016,Weinstein2017}. We may define the probability of detecting of an interaction, $D$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}). Some types of interactions will have higher detection uncertainty than others (e.g., pollination or predation often take place very quickly while parasitism can last for months or years). Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction. Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}. If these infected individuals do not happen to be included in a sample, their interactions will be missed.

      To sum up, the absence of an interaction on a given day could  be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$]. Note that some exteral factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction. Similarly, bad weather can make interactions such as pollination less likely by reducing pollinator activity~\citep{}. For those pollinators which do venture forth in poor conditions, bad weather might also  increase detection uncertainty through reduced visibility or if pollinators make shorter trips. The "forbidden links" of~\citet{Jordano2016} can also occur due to process or interaction uncertainty in our framework.

    \subsection*{Estimating detection and process uncertainty}

@@

        If we are interested only in interactions which occur in the focal system under current environmental conditions, we might use a prior which includes probabilities of co-occurrence. That is, we could limit the set of potential interactions to pairs of species which currently co-occur, condition probabilities of interaction on probabilities of co-occurrence based on abundance or habitat use, etc.~\citep{Gravel2013,Weinstein2017} Note that such models lump together interaction uncertainty and process uncertainty and are only concerned with measuring detection uncertainty. Whether or not this is appropriate will depend upon the question of interest.

>>>>

    First and foremost, ecological communities are known to be stochastic~\citep{Gotelli2000}. Community composition and abundances vary over space~\citep{Baiser2012} and time~\citep{Olesen2011a}, leading to variation in encounter probabilites and hence in interactions~\citep{Vazquez2005,Poisot2015,Graham2018}. Species must co-occur in order to be observed interacting, so any variation in co-occurrence will create variation in the set of observed interactions~\citep{Gravel2013,Graham2018}. Even assuming constant co-occurrence within a given study system, changing abundances can affect interactions if species which would otherwise interact become too rare to detect each other~\citep{Tylianakis2010,Jordano2016}. Moreover, interactions vary over space~\citep{Kitching1987,Baiser2012,Emer2018}, time~\citep{Kitching1987,Olesen2011a,Lopez2017}, between individuals~\citep{Pires2011a,Wells2013,Fodrie2015,Novak2015}, throughout life cycles~\citep{Preston2014,Clegg2018}, and with environmental conditions~\citep{Poisot2015}.

    Beyond ``true" variation in network structure, several researchers have noted the effects of sampling intensity (e.g.,~\citealp{Martinez1999,Bluthgen2006,Bluthgen2007,Jordano2016}). An assessment of the accumulation of interactions with increasing sampling effort suggests that it is even more challenging to correctly document interactions than species~\citep{Guimera2009,Poisot2012,Bartomeus2013,Jordano2016,Giron2018,Graham2018}. As a result, it has been proposed that interactions should be described probabilistically and network metrics computed accordingly~\citep{Bartomeeus2013,Poisot2016}. Efforts in this vein usually take the form of creating model food webs that approximate observed empirical networks~\citep{Allesina2008,Guimera2009,Williams2010,Rohr2016}. These models may be based on species traits and/or abundances~\citep{Rohr2016,Weinstein2017,Weinstein2017a,Graham2018} or on simple abstract rules~\citep{Allesina2008,Guimera2009,Williams2010}. Such models provide an important ''reality check'' by allowing us to test hypotheses about the factors structuring ecological networks~\citep{Bartomeus2013,Weinstein2017.Weinstein2017a,Graham2018}. They can also allow us to estimate the numbers of interactions which have not been observed~\citep{Jordano2016,Weinstein2017a} and predict which unobserved interactions are most likely~\citep{Guimera2009,Bartomeus2013}.

    [[These two paragraphs try to frame our study more clearly. Any help to shorten them?]]
    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}). Either style of model might be a poor fit for a particular study system. Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}. To provide another option for empiricists wishing to address the uncertainty in their networks, we propose a simple Bayesian framework that can easily be adapted to include whatever appropriate prior knowledge is available. This framework is designed to make the assumptions used when building networks more explicit and to quantify our uncertainty around each interaction in a network.

    First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction. In the context of this uncertainty, which can be reduced but usually not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomes2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure. We conclude with a worked example applying this framework to an intensively-sampled willow-galler network. We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks. We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.

@@

          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not~\citep{Poisot2015}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L|\mathbf{T}) = \lambda$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}. 
          In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda$.
          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}. Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{}. These examples show that we often cannot say that an interaction absolutely does not occur. Instead, an unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016,Weinstein2017}. As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. Until these gaps are filled, some uncertainty will remain about whether some species pairs could interact.

@@

          Assuming that an interaction is feasible (i.e., $L=1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}. This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a more preferred interaction partner was available~\citep{Weinstein2017a}, or substantial individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}. For example, a rare galler may not parasitize a rare plant because they do not encounter each other. In metawebs describing an interaction network found at several study sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they co-occur and interact elsewhere~\citep{}. We can define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. It is unlikely that $\chi=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur. When $\chi<1$ we cannot be sure whether an unobserved interaction did not occur and when it occurred but was not observed.

@@

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it~\citep{Jordano2016,Weinstein2017}. We may define the probability of detecting of an interaction, $D$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}). Some types of interactions will have higher detection uncertainty than others (e.g., pollination or predation often take place very quickly while parasitism can last for months or years). Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction~\citep{Wells2013}. Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}. If these infected individuals do not happen to be included in a sample, their interactions will be missed. Detection probabilities likely vary widely between species, and potentially individuals within species, due to different abundances and behaviours~\citep{Wells2013,Weinstein2017}.

      To sum up, the absence of an interaction on a given day could  be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$]. Note that some exteral factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction. Similarly, bad weather can make interactions such as pollination less likely by reducing pollinator activity~\citep{}. For those pollinators which do venture forth in poor conditions, bad weather might also  increase detection uncertainty through reduced visibility or if pollinators make shorter trips.

    \subsection*{Estimating uncertainty}

@@

        If we are interested only in interactions which occur in the focal system under current environmental conditions, we might use a prior which includes probabilities of co-occurrence. That is, we could limit the set of potential interactions to pairs of species which currently co-occur, condition probabilities of interaction on probabilities of co-occurrence based on abundance or microhabitat use, etc.~\citep{Gravel2013,Weinstein2017} Note that such models lump together the questions of whether species can interact and whether they interact at a particular site and are only concerned with measuring detection uncertainty. Whether or not this is appropriate will depend upon the question of interest.

        If traits governing interactions are known (e.g., body size in food webs~\citep{Gravel2013} or corolla depth in pollination networks~\citep{Weinstein2017a}), then trait-based models may be used as a prior. Such models estimate whether a pair of species \emph{can} interact, regardless of whether they are likely to encounter each other (although encounter probabilities and abundances can also be included, as in~\citet{Graham2018}). To address both multiple sources of uncertainty, a researcher might combine trait-based and co-occurrence models into a single prior. Such a model would reduce the uncertainty about unobserved interactions, but at the cost of adding more assumptions about the study system. This type of very detailed prior is therefore most appropriate in very well-understood systems where a great deal of expert knowledge can be applied, or in systems which are believed to follow general rules of, for example, allometric scaling~\citep{Gravel2013}. Where there is less system-specific prior knowledge, we can use prior models based on general trends in allometric scaling~\citep{Riede2011,Gravel2013}.
